Understanding the impact of electronically-delivered parenting advice

### 2019-05-15 paper/cogsci2019/cogsci2019.Rmd
minor edits

author-information: > 
    \author{{\large\bf George~Kachergis} (\texttt{kachergis@stanford.edu}) \\
    {\large\bf Hanwen Vivian~Zhang} (\texttt{vivian3@stanford.edu}) \\
    {\large\bf Michael C.~Frank} (\texttt{mcfrank@stanford.edu}) \\ 
    Department of Psychology, Stanford University \\ 
    Stanford, CA 94305 USA}

@@

Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate the findings from Experiment 1 with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)). 
We will additionally include a second control condition, in which the same activities are described in written form, rather than being demonstrated in video. 
This manipulation will help determine what the contribution of the video demonstration is in producing the observed effects on parent-child interactions.

@@

>>>>

author-information: > 
    \author{ 
      {\large\bf George~Kachergis}^1 (\texttt{kachergis@stanford.edu}) \\
      {\large\bf Emily~Hembacher}^2 (\texttt{emily.hembacher@gmail.com}) \\
      {\large\bf Veronica~Cristiano}^2 (\texttt{CRISTIANO @gallaudet.edu}) \\
      {\large\bf Hanwen Vivian~Zhang}^1 (\texttt{vivian3@stanford.edu}) \\
      {\large\bf Michael C.~Frank}^1 (\texttt{mcfrank@stanford.edu}) \\ 
    ^{1}Department of Psychology, Stanford University \\ 
    Stanford, CA 94305 USA \\
    ^{2} Nextdoor, Inc., Burlingame, CA \\
    ^{3} Gallaudet University 
    }

@@

Experiment 1 found that parents who watched a Kinedu video spoke more words overall, but had lower lexical diversity compared to parents who played with their children as they normally would at home. 
Parents who watched a Kinedu video also made more bids for joint attention, although these bids did not result in more episodes of joint attention compared to the control group. 
Experiment 2 attempts to replicate these findings from with a restricted number of preregistered predictions ([link](https://osf.io/2bpdf/)).

@@

(Table with mean and SD of tokens, types, TTR, MTLD)
